---
title: "SuccessFailure"
author: "Jgivsk"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Success failure experiment

### Data loading

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)

file_list <- list.files(path = "../Participants_Actions/", pattern = "\\.csv$", full.names = TRUE)

data_list <- lapply(file_list, function(file) {
  read.csv(file, header = TRUE, check.names = FALSE, stringsAsFactors = FALSE)
})
all_data <- do.call(rbind, data_list)

str(all_data)
colnames(all_data)

# Ensure logicals are treated properly
all_data$`AI Initiates` <- as.logical(all_data$`AI Initiates`)
all_data$`User Initiates` <- as.logical(all_data$`User Initiates`)
all_data$`Asks for Help` <- as.logical(all_data$`Asks for Help`)
all_data$Timestamp <- as.POSIXct(all_data$Timestamp)

# Fix column names to remove spaces
names(all_data) <- gsub(" ", "_", names(all_data))

```

### Plots

#### Bar graph

```{r}
# Create combined outcome and label AI Initiates as descriptive factor
plot_data <- all_data %>%
  pivot_longer(cols = c(Success, Failure), names_to = "Outcome", values_to = "Count") %>%
  group_by(AI_Initiates, Outcome, Asks_for_Help) %>%
  summarise(Count = sum(Count), .groups = "drop") %>%
  mutate(
    Combined = case_when(
      Outcome == "Success" & Asks_for_Help == 0 ~ "Success (No Help)",
      Outcome == "Success" & Asks_for_Help == 1 ~ "Success (Asked Help)",
      Outcome == "Failure" & Asks_for_Help == 0 ~ "Failure (No Help)",
      Outcome == "Failure" & Asks_for_Help == 1 ~ "Failure (Asked Help)"
    ),
    AI_Initiates_Label = factor(AI_Initiates, levels = c(0, 1), labels = c("User Initiated", "AI Initiated"))
  )

# Plot stacked bars by Combined
p <- ggplot(plot_data, aes(x = AI_Initiates_Label, y = Count, fill = Combined)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~Outcome) +
  scale_fill_manual(values = c(
    "Success (No Help)" = "steelblue",
    "Success (Asked Help)" = "blue",
    "Failure (No Help)" = "tomato",
    "Failure (Asked Help)" = "tomato"
  )) +
  labs(
    title = "Success/Failure by Initiator and Help Request (Colored by Help + Outcome)",
    x = "Who Initiated",
    y = "Count",
    fill = "Outcome + Help"
  ) +
  scale_y_continuous(breaks = seq(0, max(plot_data$Count), by = 1)) +
  theme_minimal()

ggsave("plots/SuccessFailure_Stacked_by_Help_and_Outcome_Labelled.png", plot = p, width = 8, height = 4, dpi = 300, bg = "white")

p
```

#### Session success over time
```{r plot_by_index, fig.height=3, fig.width=8}
plot_data <- all_data %>%
  arrange(Timestamp) %>%
  mutate(
    EventIndex = row_number(),
    Outcome = case_when(
      Success == 1 & User_Initiates == 1 ~ "Success User",
      Success == 1 & AI_Initiates == 1 ~ "Success AI",
      Failure == 1 & User_Initiates == 1 ~ "Failure User",
      Failure == 1 & AI_Initiates == 1 ~ "Failure AI",
      TRUE ~ "Unknown"
    )
  )

# Plot
p <- ggplot(plot_data, aes(x = EventIndex, y = 1, color = Outcome)) +
  geom_point(size = 3) +
  scale_color_manual(values = c("Success User" = "steelblue","Success AI" = "cyan", "Failure User" = "tomato","Failure AI" = "brown", "Unknown"= "grey")) +
  labs(
    title = "Session Outcomes in Sequence",
    x = "Session Index",
    y = "",
    color = "Outcome"
  ) +
    scale_x_continuous(breaks = seq(0, max(plot_data$EventIndex), by = 4)) +  # More y-axis ticks# More x-axis ticks
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.grid.major.y = element_blank())

ggsave("plots/Session Outcomes in Sequence.png", plot = p, width = 8, height = 3, dpi = 300, bg = "white")

p
```

### Statistical analysis

Understanding whether the condition changed user behavior is done by finding the ratio of success to failure in both conditions as well as their dispersion.

``` {r}
analyze <- function(successes, failures) {
  n <- successes + failures
  p <- successes / n
  sd <- sqrt(p * (1 - p) / n)
  ci_low <- p - 1.96 * sd
  ci_high <- p + 1.96 * sd
  return(list(
    success_rate = p,
    sd = sd,
    ci_95 = c(ci_low, ci_high)
  ))
}

# Summarize data into success and failures
successes <- c(sum(all_data$Success[all_data$AI_Initiates == TRUE]), sum(all_data$Success[all_data$AI_Initiates == FALSE]))

failures <- c(sum(all_data$Failure[all_data$AI_Initiates == TRUE]), sum(all_data$Failure[all_data$AI_Initiates == FALSE]))


ai_result <- analyze(successes[1], failures[1])

user_result <- analyze(successes[2], failures[2])

print(ai_result)
print(user_result)

# Create a data frame for the results
results_df <- data.frame(
  Group = c("AI Initiated", "User Initiated"),
  Successes = successes,
  Failures = failures,
  Success_Rate = c(ai_result$success_rate, user_result$success_rate),
  SD = c(ai_result$sd, user_result$sd),
  CI_Low = c(ai_result$ci_95[1], user_result$ci_95[1]),
  CI_High = c(ai_result$ci_95[2], user_result$ci_95[2])
)
# Print the results
print(results_df)

# plot the results with confidence interval
p <- ggplot(results_df, aes(x = Group, y = Success_Rate)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = CI_Low, ymax = CI_High), width = 0.15) +
  scale_y_continuous(limits = c(-0.5, 1)) +
  labs(
    title = "Success Rate by AI Initiation",
    x = "Condition",
    y = "Success Rate"
  ) +
  theme_minimal()
p
ggsave("plots/Success Rate by AI Initiation.png", plot = p, width = 8, height = 3, dpi = 300, bg = "white")
```
### Statistical analysis

As we have realatively little data we will perform a fishers exact test 
```{r}
# Create a contingency table
contingency_table <- matrix(c(
  sum(all_data$Success[all_data$AI_Initiates == TRUE]), 
  sum(all_data$Failure[all_data$AI_Initiates == TRUE]),
  sum(all_data$Success[all_data$AI_Initiates == FALSE]), 
  sum(all_data$Failure[all_data$AI_Initiates == FALSE])
), nrow = 2, byrow = TRUE)
rownames(contingency_table) <- c("AI Initiated", "User Initiated")
colnames(contingency_table) <- c("Success", "Failure")
# Perform Fisher's exact test
fisher_test_result <- fisher.test(contingency_table)
print(fisher_test_result)

```
We will also perform a chi-squared test
```{r}
# Create a contingency table
contingency_table <- matrix(c(
  sum(all_data$Success[all_data$AI_Initiates == TRUE]), 
  sum(all_data$Failure[all_data$AI_Initiates == TRUE]),
  sum(all_data$Success[all_data$AI_Initiates == FALSE]), 
  sum(all_data$Failure[all_data$AI_Initiates == FALSE])
), nrow = 2, byrow = TRUE)
rownames(contingency_table) <- c("AI Initiated", "User Initiated")
colnames(contingency_table) <- c("Success", "Failure")
# Perform Chi-squared test
chi_squared_test_result <- chisq.test(contingency_table)
print(chi_squared_test_result)
print(contingency_table)
```
